Appendix for: Deep Reinforcement Learning for Conservation Decisions

### 2021-04-09 manuscript/appendix.Rmd
update requirements.txt

```{r setup, cache = FALSE, message=FALSE}
library(tidyverse)
library(patchwork)
library(reticulate)

np <- import("numpy")
np$random$seed(42L)

# force CPU-evaluation if needing perfect reproducibility
Sys.setenv("CUDA_VISIBLE_DEVICES"="0")

@@

```{r }
## Python dependencies
gym         <- import ("gym")
gym_fishing <- import("gym_fishing")
sb3         <- import ("stable_baselines3")

## initialize the environment
env <- gym$make("fishing-v1", sigma = 0.1)
```

```{r eval=!file.exists("cache/td3.zip")}
# train an agent (model) on one of the environments:

#Trial 15 finished with value: 7.6994757652282715 and parameters: 
hyper = list('gamma'= 0.995, 'lr'= 0.0001355522450968401, 'batch_size'= 128L, 
         'buffer_size'= 10000L, 'episodic'= FALSE, 'train_freq'= 128L, 
         'noise_type'= 'normal', 'noise_std'= 0.6656948079225263, 
         'net_arch'= 'big')
policy_kwargs = list(net_arch=c(400L, 300L)) # big

#non-episodic:
hyper['gradient_steps'] = hyper['train_freq']
hyper['n_episodes_rollout'] = -1
n_actions = env$action_space$shape[0]
hyper$action_noise = sb3$common$noise$NormalActionNoise(
        mean=np$zeros(n_actions),
        sigma= hyper[['noise_std']] * np$ones(n_actions)
        )

td3 = sb3$TD3('MlpPolicy', env,  verbose=0L, seed = 42L,
            gamma = hyper[['gamma']],
            learning_rate = hyper[['lr']],
            batch_size = hyper[['batch_size']],            
            buffer_size = hyper[['buffer_size']],
            action_noise = hyper[['action_noise']],
            train_freq = hyper[['train_freq']],
            gradient_steps = hyper[['train_freq']],
            n_episodes_rollout = hyper[['n_episodes_rollout']],
            policy_kwargs=policy_kwargs)

td3$learn(total_timesteps=300000L)
td3$save("cache/td3")
```

@@

@@

```{r}
gym_conservation <- import("gym_conservation")
env <- gym$make("conservation-v6")
```

```{r}
# Simulate management under the trained agent
# See https://github.com/boettiger-lab/conservation-agents/blob/4baaa6c9b994085ca56c42364f7affcc58b0ef3b/conservation/TD3.py

>>>>

```{r setup, cache = FALSE, message=FALSE}
# R dependencies
library(tidyverse)
library(patchwork)
library(reticulate)

## Python dependencies loaded via R
sb3         <- import ("stable_baselines3")
gym         <- import ("gym")
gym_fishing <- import("gym_fishing")
gym_conservation <- import("gym_conservation")

## reproducible settings
np <- import("numpy")
np$random$seed(42L)
# Set to "" to force CPU-evaluation if needing perfect reproducibility
Sys.setenv("CUDA_VISIBLE_DEVICES"="")

@@

```{r }
## initialize the environment
env <- gym$make("fishing-v1", sigma = 0.1)
```

We train the A2C algorithm using default hyper-parameter settings, based on the original publication [@A2C; @SB3].  While default hyperparameters provide a useful starting place (particularly when the environment has been suitably normalized, a best-practice we discuss above), better performance can almost always be achived by _tuning_ the hyperparameter selection.

@@

Hyperparameters are selected through the process of model tuning, see.

```{r}
# train an agent (model) on one of the environments:
hyper = list('gamma'= 0.995, 'lr'= 0.0001355522450968401, 'batch_size'= 128L, 
         'buffer_size'= 10000L, 'episodic'= FALSE, 'train_freq'= 128L, 
         'noise_type'= 'normal', 'noise_std'= 0.6656948079225263, 
         'net_arch'= 'big')
policy_kwargs = list(net_arch=c(400L, 300L)) # "big"

#non-episodic:
hyper['gradient_steps'] = hyper['train_freq']
hyper['n_episodes_rollout'] = -1 # deprecated in latest SB3
n_actions = env$action_space$shape[0]
hyper$action_noise = sb3$common$noise$NormalActionNoise(
        mean=np$zeros(n_actions),
        sigma= hyper[['noise_std']] * np$ones(n_actions)
        )

td3 = sb3$TD3( 'MlpPolicy', 
               env,  
               verbose=0L, 
               seed = 42L,
               policy_kwargs=policy_kwargs,
               learning_rate = hyper[['lr']],
               gamma = hyper[['gamma']],
               batch_size = hyper[['batch_size']],            
               buffer_size = hyper[['buffer_size']],
               action_noise = hyper[['action_noise']],
               train_freq = hyper[['train_freq']],
               gradient_steps = hyper[['train_freq']],
               n_episodes_rollout = hyper[['n_episodes_rollout']]
              )
```

```{r eval=!file.exists("cache/td3.zip")}
td3$learn(total_timesteps=300000L)
td3$save("cache/td3")
```

@@

```{r}
env <- gym$make("conservation-v6")
```

```{r}
# Simulate management under the trained agent
# See https://github.com/boettiger-lab/conservation-agents/blob//conservation/TD3-v6.py
